---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# dyntoy

dyntoy simulates single-cell expression data in which a single-cell trajectory is present. Even though the model to generate the data is very simplistic (and far from realistic), it can simulate very complex trajectory models, such as large trees, convergences and loops.

As the data is relatively easy, it can be used to quickly test and prototype a [TI method](https://github.com/dynverse/dynmethods). However, for more realistic synthetic data, check out our [dyngen package](https://github.com/dynverse/dyngen).

## Installation

Install using devtools:

```{r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("dynverse/dyntoy")
```


## Example

dyntoy contains some pre-generated toy data within the `toy_tasks` data object:

```{r}
data("toy_tasks", package = "dyntoy")
```

Data can be generated using `generate_dataset`:

```{r}
library(dyntoy)
task <- generate_dataset(
  model = model_bifurcating(num_branchpoints = 2),
  num_cells = 1000,
  num_genes = 1000
)

task$milestone_network
```

## Related work

- PROSSTT: https://github.com/soedinglab/prosstt
- Splatter: https://github.com/Oshlack/splatter
